Portfolios of Subgraph Isomorphism Algorithms

### 2015-12-08 paper/paper.tex
updated figures

\begin{table}[ht]
\centering
\begin{tabular}{lr}
  \toprule
& mean runtime\\
  \midrule
virtual best & 5822.809\\
  single best & 7782.569\\
  LLAMA & 6595.275\\
   \bottomrule
\end{tabular}
\vspace{1ex}
\caption{Algorithm selection performance on reduced set of 2336
instances.}\label{tab:res}
\end{table}

@@

\begin{table}[ht]
\centering
\begin{tabular}{lr}
  \toprule
& mean runtime\\
  \midrule
virtual best & 2375.913\\
  single best & 3177.569\\
  LLAMA & 2706.330\\
   \bottomrule
\end{tabular}
\vspace{1ex}
\caption{Algorithm selection performance on the full set of 5725
instances.}\label{tab:resfull}
\end{table}

@@

>>>>

\begin{table}[ht]
\centering
\begin{tabular}{lr}
  \toprule
& mean runtime\\
  \midrule
virtual best & 5822.809\\
  single best & 7788.719\\
  LLAMA & 6509.947\\
   \bottomrule
\end{tabular}
\vspace{1ex}
\caption{Algorithm selection performance on reduced set of 2336
instances.}\label{tab:res}
\end{table}

@@

\begin{table}[ht]
\centering
\begin{tabular}{lr}
  \toprule
& mean runtime\\
  \midrule
virtual best & 2375.913\\
  single best & 3177.569\\
  LLAMA & 2706.749\\
   \bottomrule
\end{tabular}
\vspace{1ex}
\caption{Algorithm selection performance on the full set of 5725
instances.}\label{tab:resfull}
\end{table}

@@

Figure~\ref{fig:portfolio-ecdf} shows the cumulative density function for the
individual solvers, the virtual best solver, and the LLAMA portfolio. The
virtual best solver clearly dominates with a significant margin to the next
best. VF2 is far below all other solvers. The portfolio does not perform well
for instances that can be solved quickly because of the overhead incurred
through feature computation. As the instances become more difficult to solve,
its performance improves. For instances that take more than 1,000 seconds to
solve, the portfolio eclipses any individual solver and closes most of the gap
to the virtual best solver.

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{figures/portfolio-ecdf}
\caption{Empirical cumulative density function of solvers, virtual best solvers,
and the LLAMA portfolio.}
\label{fig:portfolio-ecdf}
\end{figure}
